\documentstyle[12pt]{article}
\title{GSoC 2014 Application for SciRuby}
\author{Arun Kumar M S, Long Beach, CA}

\begin{document}

\section{Contact information}
Email address : arun.einstein@gmail.com
GitHub Username: aruneinstein
Approximate Physical Location: Long Beach, CA.

\section{Why do you like Ruby, and why do you want to work on SciRuby?}

\section{What do you like about science and why? What area do you like best?}

\section{Describe your experience with the following: Ruby, C, C++, other languages.}

\section{Describe your educational background (school, degree plan, major, past degrees, research area, etc.).}

\section{Have you offered any pull requests for SciRuby or contributed in other ways? Please provide links, if possible. Past contributions are not essential, but are highly recommended.}

\section{What other commitments do you have this summer aside from GSoC? What obstacles do you foresee this summer as far as contributing the full forty hours per week during the GSoC period?}

\section{Please propose a project you would like to work on. Successful proposals will require advanced planning, communication with the project administrators and mentors, and likely a great deal of research on specific methods for achieving your project goals (e.g., what algorithms will you use? What frameworks?). A good place to start is the Ideas Page. You should also consider lurking on our IRC channel (sciruby on FreeNode). Participation in listserv discussions is strongly recommended.}

\section{Please provide a specific timeline for your project from application period until pencils-down. What benchmarks will you set for yourself? The greater the detail on this question and the previous, the better.}

\section{What is one long-term vision for something you'd like scientific software to be able to do. Think big picture, not necessarily realistic in the short term.}

\section{What are your hobbies, aside from coding? Tell us a little about yourself that isn't reflected in the rest of your application. What do you want to do with your life (if you have any idea)?}

\section{What else do you think we should have asked but didn't? Propose a question of your own and answer it here.}

\section{One aim of the SciRuby foundation is to increase diversity in open source science software development. How do we get more women interested in open source software development and science?}

\end{document}
